Transfer Learning in Visual and Relational Reasoning

### 2020-02-07 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
no message

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}

We follow the notations in the survey by~\cite{pan2009survey}.
A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
For visual reasoning problems considered in this paper, 
$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or 
a combination of both visual inputs and questions in other cases. 
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
question\footnote{%
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
	only a single answer is needed for the entire video.}. % 
If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
defines a separate task.

@@

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}
Due to the complex nature of visual reasoning, it turns out that
transfer learning from a source domain to a target domain can be investigated in 
multiple ways depend on how the features are related between the two domains, including attributes such as size, color and shape, as well as temporal characteristics reflected in the number of frames and the scene complexity.
To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
For visual reasoning problems considered in this paper, 
$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or 
a combination of both visual inputs and questions in other cases. 
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
question\footnote{%
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
	only a single answer is needed for the entire video.}. % 
If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
defines a separate task.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer}, 
and \emph{reasoning transfer}. 
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
investigations of transfer learning.
In the next section we detail the performance of
SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
for feature transfer, the COG dataset for temporal transfer, and finally
both datasets for reasoning transfer, with appropriate baseline comparisons.

Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.
